Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
Extended threats to validity.

The experimental evaluation in section~\ref{experimental-results} shows
a very positive evaluation of \tool over a diverse set of real-world
benchmarks. Nevertheless, the set of benchmarks is limited within the
scope of this paper and \tool's performance may not generalise to other
benchmark scenarios.

@@

>>>>

The experimental evaluation in section~\ref{experimental-results} outlines
a very positive assessment of \tool over a diverse set of real-world
benchmarks. Nevertheless, the set of benchmarks is limited within the
scope of this paper and \tool's performance may not generalise to other
benchmark scenarios. This can be addressed by expanding the benchmark set
based on available literature in future experiments.

@@

Finally, the experimental results we attained using \tool with
regard to stability properties may not generalise to other properties
expressed over the controller to synthesize. The inductive nature of the
two-stage back-end of \tool increases performance significantly compared to the
one-stage back-end, but this performance benefit introduced by CEGIS'
inductive generalisations may not perform equally well for other controller
properties. Additional experiments are necessary to confirm that the performance
of our inductive synthesis approach can be leveraged in those scenarios as well.
